Essays in \\Computational Management Science

### 2018-05-11 Chapters/hathor-bitcoin-math.tex
Changes in Hathor's bitcoin math, acknowledgments, and bass model.

\section{Fork analysis}

@@

When a disagreement between miners' rules happens, that is referred as either a hard-fork or a soft-fork. It is said to be a soft-fork when the rules are backward compatible, and a hard-fork when the rules are not backward compatible. In general, a hard-fork relaxes the constraints, while the latter hardens them.

Suppose that the miners' are split in two groups, $G_1$ and $G_2$, with different rules. Let's say $H_1$ and $H_2$ are their hash rate, respectively. We have two different scenarios to analyze: (i) when neither of them accepts other's blocks; and (ii) when $G_2$ accepts $G_1$'s blocks, but not the other way around.

Scenario (i) is easy to analyze, as the network would split and, after a while, both difficulties will be adjusted. Then, they will be just like two different Bitcoin networks.

Scenario (ii) is more trick. As $G_2$ accepts $G_1$ blocks, their hashrate will matter. If $H_1 > H_2$, then $G_2$ will frequently skip their blockchain, because $G_1$'s blockchain will be longer most of the time. If $H_1 < H_2$, then $G_2$ may have its own blockchain after a while --- a true fork. But what would happen if $H_1$ keeps increasing and eventually gets larger than $H_2$? It if happens for sufficient time, the whole $G_2$'s blockchain may be discarded in order to move to $G_1$'s blockchain when $G_1$'s gets longer.

\begin{theorem}
	When $H_1 > H_2$, the
\end{theorem}

>>>>

%\section{Fork analysis}

@@

%When a disagreement between miners' rules happens, that is referred as either a hard-fork or a soft-fork. It is said to be a soft-fork when the rules are backward compatible, and a hard-fork when the rules are not backward compatible. In general, a hard-fork relaxes the constraints, while the latter hardens them.

%Suppose that the miners' are split in two groups, $G_1$ and $G_2$, with different rules. Let's say $H_1$ and $H_2$ are their hash rate, respectively. We have two different scenarios to analyze: (i) when neither of them accepts other's blocks; and (ii) when $G_2$ accepts $G_1$'s blocks, but not the other way around.

%Scenario (i) is easy to analyze, as the network would split and, after a while, both difficulties will be adjusted. Then, they will be just like two different Bitcoin networks.

%Scenario (ii) is more trick. As $G_2$ accepts $G_1$ blocks, their hashrate will matter. If $H_1 > H_2$, then $G_2$ will frequently skip their blockchain, because $G_1$'s blockchain will be longer most of the time. If $H_1 < H_2$, then $G_2$ may have its own blockchain after a while --- a true fork. But what would happen if $H_1$ keeps increasing and eventually gets larger than $H_2$? It if happens for sufficient time, the whole $G_2$'s blockchain may be discarded in order to move to $G_1$'s blockchain when $G_1$'s gets longer.

%\begin{theorem}
%	When $H_1 > H_2$, the
%\end{theorem}

### 2018-05-11 FrontBackmatter/Acknowledgments.tex
Changes in Hathor's bitcoin math, acknowledgments, and bass model.

Thanks to my wife, Patrícia, for sharing the dreams, the passion, and the craziness, for all her caring and love. Especially, for understanding my absence.

I'm very grateful for the friendship, guidance, and invaluable help of my advisor Alexandre Linhares. Without him this work would never be possible. His passion for cognitive sciences, artificial intelligence, and economics has influenced everyone around him. His ideas have profoundly influenced my thoughts and my life since we have met. I must not forget his wife Paula, who became a dear friend and has always supported me as well, even when I was working in her living room until the sunrise. Thank you for this amazing journey, my friends.

Thanks to my dear friends Daniel Chada, Layla Mendes, Renato Kogeyama, André Luiz, Luiz Sacramento, Kaillen Givigi, Jamil Chivitarese, Lucia Barros, Daniel Modenesi, Bernardo Machado, always available for serious talking, laughing, and sharing their wide and deep knowledge, even at lunchtime and weekends. I will never forget our all-you-can-eat adventures in Bros restaurant, the snacks in Catarina, and the drinks in Bigode bar. You have become close friends who I will carry for life.

Thanks to my long-time partner and dear friend Claudio Abreu, who always encouraged me to take risks and to improve myself. He is the most fearless person I have ever met.

Thanks to EBAPE / FGV for their great faculty, staff, and infrastructure. A special thanks to Celene Silva Melo for her empathy and support besides all the help with paperwork, funding, and many other things. Another special thanks to doctor Luiz Antônio Joia, who trusted me in the first place and guided my first steps into the world of academy.

>>>>

Thanks to my wife, Patrícia, for sharing the dreams, the passion, and the craziness, for all her caring and love. Especially, for understanding my absence and my unusual working times. Her loyalty and commitment make me the luckiest man alive. I love you.

I'm very grateful for the friendship, guidance, and invaluable help of my advisor Alexandre Linhares. Without him this work would never be possible. His passion for cognitive sciences, artificial intelligence, and economics has influenced everyone around him. His ideas have profoundly influenced my thoughts and my life since we have met. His optimism and trust in my abilities were undying. I must not forget his wife Paula, who became a dear friend and has always supported me as well, even when I was working in her living room until sunrise. Thank you for this amazing journey, my friends.

Thanks to my friends Layla Mendes, Renato Kogeyama, André Luiz, Luiz Sacramento, Kaillen Givigi, Jamil Chivitarese, Lucia Barros, Daniel Modenesi, Bernardo Machado, and Andréia Sodré, always available for serious talking, laughing, and sharing their wide and deep knowledge, even at lunchtime and weekends. I will never forget our all-you-can-eat adventures in Bros restaurant, the snacks in Catarina, and the drinks in Bigode's bar. You have become close friends who I will carry for life.

Thanks to my long-time business partner and friend Claudio Abreu, who share a deep delight for engineering and has taught me so much about life, family, and business. He has always put faith in me and cheered for my victories. Thank you, my dear friend.

I thank my dear buddy and coauthor Daniel Chada for sharing the passion for research, always inspiring and amusing me with his astonishing ideas. Our long discussions have definitely shaped my researching abilities. Thank you, bro!

Thanks to EBAPE / FGV for their finest faculty, staff, and infrastructure. A special thanks to Celene Silva Melo for her empathy and support besides all the help with paperwork, funding, and many other things. Another special thanks to professor Luiz Antônio Joia, who trusted me in the first place and guided my first steps into the world of academy.

Last, but far from least, I thank Kallen Givigi for being the ``Psych-os'' lab's protector and defender. She has always been there solving all sort of things (even personal matters) and whipping our lab into shape. Always kind and smiling, she gently asked for more focus and less mess. Your request is my command, my lady.
